---
title: "Model_Testing"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages("readxl")
install.packages("dplyr")
install.packages("ggplot2")
install.packages("tidyverse")
knitr::opts_chunk$set(echo = TRUE)
library("readxl")
library("dplyr")
library("ggplot2")
library("tidyverse")
```
Reading data from datasheets:
```{r}
abbrev = c('AL', 'AK', 'AZ', 'AR', 'CA', 'CO', 'CT', 'DE', 'DC', 'FL', 'GA', 'HI', 'ID', 'IL', 'IN', 'IA', 'KS', 'KY', 'LA', 'ME', 'MD', 'MA', 'MI', 'MN', 'MS', 'MO', 'MT', 'NE', 'NV', 'NH', 'NJ', 'NM', 'NY', 'NC', 'ND', 'OH', 'OK', 'OR', 'PA', 'RI', 'SC', 'SD', 'TN', 'TX', 'UT', 'VT', 'WA', 'WV', 'WI', 'WY')
df1 = read_excel("food.xlsx","AL")
df2 = read_excel("food.xlsx","AK")
df3 = read_excel("food.xlsx","AZ")
df4 = read_excel("food.xlsx","AR")
df5 = read_excel("food.xlsx","CA")
df6 = read_excel("food.xlsx","CO")
df7 = read_excel("food.xlsx","CT")
df8 = read_excel("food.xlsx","DE")
df9 = read_excel("food.xlsx","DC")
df10 = read_excel("food.xlsx","FL")
df11 = read_excel("food.xlsx","GA")
df12 = read_excel("food.xlsx","HI")
df13 = read_excel("food.xlsx","ID")
df14 = read_excel("food.xlsx","IL")
df15 = read_excel("food.xlsx","IN")
df16 = read_excel("food.xlsx","IA")
df17 = read_excel("food.xlsx","KS")
df18 = read_excel("food.xlsx","KY")
df19 = read_excel("food.xlsx","LA")
df20 = read_excel("food.xlsx","ME")
df21 = read_excel("food.xlsx","MD")
df22 = read_excel("food.xlsx","MA")
df23 = read_excel("food.xlsx","MI")
df24 = read_excel("food.xlsx","MN")
df25 = read_excel("food.xlsx","MS")
df26 = read_excel("food.xlsx","MO")
df27 = read_excel("food.xlsx","MT")
df28 = read_excel("food.xlsx","NE")
df29 = read_excel("food.xlsx","NV")
df30 = read_excel("food.xlsx","NH")
df31 = read_excel("food.xlsx","NJ")
df32 = read_excel("food.xlsx","NM")
df33 = read_excel("food.xlsx","NY")
df34 = read_excel("food.xlsx","NC")
df35 = read_excel("food.xlsx","ND")
df36 = read_excel("food.xlsx","OH")
df37 = read_excel("food.xlsx","OK")
df38 = read_excel("food.xlsx","OR")
df39 = read_excel("food.xlsx","PA")
df40 = read_excel("food.xlsx","RI")
df41 = read_excel("food.xlsx","SC")
df42 = read_excel("food.xlsx","SD")
df43 = read_excel("food.xlsx","TN")
df44 = read_excel("food.xlsx","TS")
df45 = read_excel("food.xlsx","UT")
df46 = read_excel("food.xlsx","VT")
df47 = read_excel("food.xlsx","WA")
df48 = read_excel("food.xlsx","WV")
df49 = read_excel("food.xlsx","WI")
df50 = read_excel("food.xlsx","WY")
food = list("AL"=df1,"AK"=df2,"AZ"=df3,"AR"=df4,"CA"=df5,"CO"=df6,"CT"=df7,"DE"=df8,"DC"=df9,"FL"=df10,"GA"=df11,"HI"=df12,"ID"=df13,"IL"=df14,"IN"=df15,"IA"=df16,"KS"=df17,"KY"=df18,"LA"=df19,"ME"=df20,"MD"=df21,"MA"=df22,"MI"=df23,"MN"=df24,"MS"=df25,"MO"=df26,"MT"=df27,"NE"=df28,"NV"=df29,"NH"=df30,"NJ"=df31,"NM"=df32,"NY"=df33,"NC"=df34,"ND"=df35,"OH"=df36,"OK"=df37,"OR"=df38,"PA"=df39,"RI"=df40,"SC"=df41,"SD"=df42,"TN"=df43,"TX"=df44,"UT"=df45,"VT"=df46,"WA"=df47,"WV"=df48,"WI"=df49,"WY"=df50)
```

Checking to see if any states have NULL values for any of the variables(if yes then we do not consider them):
```{r}
vars <- c("TractSNAP","TractLOWI","TractKids","TractSeniors","PovertyRate","TractAsian","TractNHOPI","TractAIAN","TractHispanic","TractHUNV","TractBlack","TractWhite")
useless <- c(2,42,44)
useful <- c(1:50)
useful<-useful[-useless]
useful
```


Only Alaska, South Dakota and Texas are unable to be used in the data due to either NULL values for some of our model variables or the non-existence of some of our model variables

Now we can use our model from California to predict other state values

Making Linear Model:
```{r}
vars <- c("TractSNAP","Pop2010","LowIncomeTracts","PovertyRate","LA1and10","LATracts1","TractLOWI ","TractKids","TractSeniors","TractWhite","TractBlack","TractAsian", "TractNHOPI", 
    "TractAIAN","TractOMultir", "TractHispanic", "TractHUNV","State","County")
food_data <- rbind(food$CA,food$NY,food$KS)
rcols <- c()
for (i in 1:ncol(food_data)){
  if (any(is.na(food_data[,i]))){
    rcols <- append(rcols,i)
  }
}
food_data <- food_data[-rcols]
for (i in 1:ncol(food_data)){
  if (any(food_data[,i]=='NULL')){
    rcols <- append(rcols,i)
  }
}
food_data <- food_data[-rcols]
nreg_f<-lm(formula=TractSNAP~TractLOWI+TractKids+TractSeniors+PovertyRate+TractAsian+TractNHOPI+TractAIAN+TractHispanic+TractHUNV+TractBlack+TractWhite,data=food_data)
summary(nreg_f)
nreg_f$terms
```

Making error percentages for each State's counties
```{r}
for (i in useful){
  food[[i]]$ERR <- (predict(nreg_f,food[[i]])-food[[i]]$TractSNAP)/(food[[i]]$TractSNAP)
}
```
Boxplot test of data:
```{r}
food_states <- food[[1]]
for (states in useful){
  if (states!=1){
    food_states <- rbind(food_states, food[[states]],by=vars)
  }
}
food_states
```